Fitting Synchrotron Models to Gamma-Ray Burst Data from INTEGRAL/SPI

### 2021-11-30 src/ms.tex
add ts figures

% Filler text
\usepackage{blindtext}

% Begin!
\begin{document}

@@

As we are introducing a new analysis software in this work, we want to compare it to the existing analysis software, to check if the results are in agreement. Therefor we shortly summarize the official analysis tools for GRB analysis, which are part of the INTEGRAL Offline Scientific Analysis (OSA) software, here.

Analyzing GRB data from SPI with the OSA tools is a multi step process. The first steps are basic and cover selecting the science window with the GRB, the time intervals for active time and background time as well as the energy bins for the analysis. After that one can either find the location of the GRB with SPIROS or set it manually, if it is already known. The next steps concern the spectral fitting, which is done in a two step procedure, which will be called 'Photo Peak Fitting' and 'Energy Redistribution Fitting' hereafter.

@@

The first step in the spectral fitting with OSA, is to use only the photo peak response of the detectors. These responses depend on the source position, as this defines for example the absorption by the mask. With these responses and the measured data in the individual SPI detectors, taking into account the different background rates, a photon flux is fitted individually per energy channel. These pseudo photon fluxes are not the final result, as up to this point energy dispersion and resolution was ignored.

@@

The pseudo photon flux data points from the 'Photo Peak Fitting' step, which are no real data points anymore, are fitted with a photon model which gets folded through a correction response, that was created by OSA. This correction response depends on the source position and energy bins that are used and should account for energy dispersion as well as resolution. In this step the energy channels are fitted simultaneously, as it is impossible to incorporate energy dispersion in a way that fits every energy channel individually. This fitting can be done in different spectral fitting software like 3ML or XSPEC. In this work we always used 3ML.

@@

In this work we analyze GRB 120711A, which was a bright, multi pulse GRB with a precursor and a long emission period of $\approx$100 seconds. It was detected by SPI and GBM. In this work we only look at one time slice with a duration of 10 seconds around the highest peak in the light curves (add light curve plot with SPI and GBM data).

>>>>

% Filler text
\usepackage{caption}
\usepackage{subcaption}
% Begin!
\begin{document}

@@

As we are introducing a new analysis software in this work, we want to compare it to the existing analysis software, to check if the results are in agreement. We shortly summarize the official analysis tools for GRB analysis, which are part of the INTEGRAL Offline Scientific Analysis (OSA) software. (https://ui.adsabs.harvard.edu/abs/2003A%26A...411L..53C/abstract)

Analyzing GRB data from SPI with the OSA tools is a multistep process. The first steps are basic and cover selecting the science window with the GRB, the time intervals for active time and background time as well as the energy bins for the analysis. After that one can either find the location of the GRB with SPIROS, i.e. an iterative source removal algorithm for SPI data, or set it manually, if it is already known. The next steps concern the spectral fitting, which is done in an other two-step procedure, which will be called 'Photo Peak Fitting' and 'Energy Redistribution Fitting' hereafter.

@@

The first step in the spectral fitting with OSA is to use only the photo peak response of the detectors. These responses depend on the source position, as this defines for example the absorption by the mask. With these responses and the measured data in the individual SPI detectors, taking into account the different background rates, a photon flux is fitted individually per energy channel. These pseudo photon fluxes are not the final result, as up to this point energy dispersion and detector energy resolution was ignored.

@@

The pseudo photon flux data points from the 'Photo Peak Fitting' step, which are no real data points anymore, are fitted with a spectral photon flux model which is convolved with a correction response, which is also available through OSA. This correction response depends on the source position and energy bins that are used and should account for energy dispersion as well as resolution. In this step the energy channels are fitted simultaneously, as it is impossible to incorporate energy dispersion in a way that fits every energy channel individually. This fitting can be done in different spectral fitting software like 3ML or XSPEC. In this work we always used 3ML.

@@

In this work we analyze GRB 120711A, which was a bright, multi pulse GRB with a precursor and a long emission period of $\approx$100 seconds. It was detected by SPI and GBM. In this work we only look at one time slice with a duration of 10 seconds around the highest peak in the light curves

\begin{figure}
  \begin{centering}
    \begin{subfigure}[b]{1\textwidth}
      \begin{centering}
        \includegraphics{figures/spi_lightcurve_ts.pdf}
        \caption{Light curve for SPI detector 0 and GRB120711A.}
        \label{fig:ts_spi}
      \end{centering}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{1\textwidth}
      \begin{centering}
        \includegraphics{figures/gbm_lightcurve_ts.pdf}
        \caption{Light curve for GBM detector n2 and GRB120711A.}
        \label{fig:ts_gbm}
      \end{centering}
    \end{subfigure}
  \end{centering}
\end{figure}
